Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-16 docs/paper.tex
Worked on describing comparison, added references to peer group papers

	%To avoid this, the MDD search could be changed to start at the maximal depth and search for a way towards the start node, which by start uniqueness remains without vertex conflicts.
	%Two strategies could be used to avoid this: firstly, the MDD search could be changed to start at the maximal depth and search for a way towards the start (which by start uniqueness is always non-conflicting); secondly, a bipartite matching algorithm could be employed to see if any matching exists between agents and goals they can reach. An advantage of the former strategy is that it will, in particular with larger team sizes, reduce the number of maximal depth nodes drastically, so that the subsequent search is from few nodes to one goal. By only running a matching algorithm to skip regular MDD search, there is no such reduction so from one starting position paths will be searched to potentially an exponential number of goal nodes, of which many will end up being illegal. 
	%[TODO: just focus on explaining why inverted MDD search was/could be used to solve this? Or just toss this out for lack of time/space. Why didn't I come up with this idea earlier...]
	\subsection{General optimizations}

	To improve both types of algorithms, some general optimizations were found that can be used to speed up the search that are here motivated. 
	\subsubsection{Bounds in ID}
	\begin{property}[Lower bound]
		When merging groups $g_i,g_j$ with solution costs $C_i,C_j$ to yield group $g_k$, for any solution for this group with cost $C_k$
		\[C_k\geq C_i + C_j\]
	\end{property}
	\begin{proof}
		Assume there would be a solution with $C_k < C_i + C_j$. Taking $C_k^i$ to denote the SIC of agents that used to make up $g_i$ in the solution to $g_k$, without loss of generality $C_k^i < C_i$, which contradicts the optimality of the solution with cost $C_i$ for $g_i$ independent of $g_j$.
	\end{proof}
	\begin{property}[Reduced upper bound]
		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
	\end{property}
	\subsubsection{Child pruning}
	In the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation. However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented. This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, which can drastically improve the (average) branching factor as $k$ increases.
	\begin{property}[Incompatibility with enhanced pruning]
		Enhanced pruning combined with child pruning (hereafter E+C pruning) is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
	\end{property}
	\begin{figure}[H]
	\centering
	\begin{subfigure}{0.40\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-ep-2}
		\caption{Instance}
		\label{fig:counter-example:a}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-tree}
		\caption{Pruned ICT that is traversed}
		\label{fig:counter-example:b}
	\end{subfigure}
	\caption{Counter-example for E+C pruning}
	\label{fig:counter-example}
	\begin{proof}
		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$. It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.  Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$. Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality. $(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path. $(r,b)$ will not change either MDD in this node. When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated. By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed. Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
	\end{proof}
	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
	\centering
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
		\caption{25, 1 team}
		\label{fig:25-1-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
		\caption{25, 3 teams}
		\label{fig:25-3-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
		\caption{75, 1 team}
		\label{fig:75-1-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
		\caption{75, 3 teams}
		\label{fig:75-3-p}
	\end{subfigure}
	\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
	\label{fig:probs}
	\end{figure*}
	\begin{figure*}[t]
	\centering
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
		\caption{25, 1 team}
		\label{fig:25-1-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
		\caption{25, 3 teams}
		\label{fig:25-3-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
		\caption{75, 1 team}
		\label{fig:75-1-p}
	\end{subfigure}
	\begin{subfigure}{0.44\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
		\caption{75, 3 teams}
		\label{fig:75-3-p}
	\end{subfigure}
	\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
	\label{fig:probs}
	\end{figure*}

\restoregeometry

	\section{Results}
	\label{experiments}
	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant (Exh+E+B+O) is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}. The values compared are the fraction of instances solved, and the average runtime per instance. It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
	\subsection{Experimental setup}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists. For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge. This observation informed the creation of a map generator within the peer group with various parameters. Using this map generator, two types of 20x20 grids were generated:
	\begin{enumerate}
		\item 25: a grid with 25\% of tiles being obstacles.
		\item 75: a grid with 75\% of tiles being obstacles. 
	\end{enumerate}
	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams strictly speaking for the datapoints with respectively $1,2$ agents).

@@

	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
	Figure \ref{fig:probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings. The meaning of the abbreviations used in the legend are as follows:
	\begin{itemize}
		\begin{minipage}{0.45\linewidth}
			\item S: Simple pruning
			\item E: Enhanced pruning
			\item C: Child pruning
		\end{minipage}
		\begin{minipage}{0.45\linewidth}
			\item ID: Independence detection
			\item B: Bounded search
			\item O: Approximate ordered enumeration
		\end{minipage}
	\end{itemize}
	\subsubsection{Analysis}
	Across exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:25-3-p}. Almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E. Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less. Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}. Although no bound-value data was recorded, one explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed.

	Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method. In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:75-1-p},\ref{fig:75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often.

	Ordered enumeration with ID performs much better in \ref{fig:75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:25-1-p},\ref{fig:75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID, which is is more typical.

	With some exceptions, ICTS-m variants are outperformed by the exhaustive variants.
	In almost every instance the ICTS-m variants are outperformed by exhaustive variants. 
	\subsection{Experiment 2: Algorithms for MAPFM}
	[TODO: add relative comparison]

	\section{Discussion}

%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.

	Compared to the results achieved by \cite{ma2016}, the results recorded are somewhat disappointing.
	\section{Conclusions}
	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS. In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired. Exhaustive methods, like those discussed in detail in \ref{exhaustive}, cannot be expected to scale well as teams grow larger due to their complexity, no matter what optimizations are put in place. Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms. It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out. Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a very long way to go before being usable in practical scenarios with significant problem sizes.
	\section{Future work}
	In this project, there were many roads not taken. In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures or ways to exploit the fact that agents are partitioned into teams. For instance, the hungarian algorithm could be used to find lower-bounds for per-team SICs, which allows skipping the low-level search in many cases and can trivially be combined with pruned child generation branching within teams.

@@

	\printbibliography
	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25, 1 team}
			\label{fig:25-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25, 3 teams}
			\label{fig:25-3}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75, 1 team}
			\label{fig:75-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75, 3 teams}
			\label{fig:75-3}
		\end{subfigure}
		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
		\label{fig:times}
	\end{figure*}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25, 1 team}
			\label{fig:25-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25, 3 teams}
			\label{fig:25-3-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75, 1 team}
			\label{fig:75-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75, 3 teams}
			\label{fig:75-3-p}
		\end{subfigure}
		\caption{Average solving time on two types of 20x20 grids with a 120s timeout}
		\label{fig:probs}
	\end{figure*}

>>>>

	%To avoid this, the MDD search could be changed to start at the maximal depth and search for a way towards the start node, which by start uniqueness remains without vertex conflicts.
	%Two strategies could be used to avoid this: firstly, the MDD search could be changed to start at the maximal depth and search for a way towards the start (which by start uniqueness is always non-conflicting); secondly, a bipartite matching algorithm could be employed to see if any matching exists between agents and goals they can reach. An advantage of the former strategy is that it will, in particular with larger team sizes, reduce the number of maximal depth nodes drastically, so that the subsequent search is from few nodes to one goal. By only running a matching algorithm to skip regular MDD search, there is no such reduction so from one starting position paths will be searched to potentially an exponential number of goal nodes, of which many will end up being illegal. 
	%[TODO: just focus on explaining why inverted MDD search was/could be used to solve this? Or just toss this out for lack of time/space. Why didn't I come up with this idea earlier...]
	\subsection{Optimizations}
	To improve both types of algorithms, some optimizations were found that can be used to speed up the search. These are here motivated. 
	\subsubsection{Bounds in ID}
	Information gained about solution costs of independent groups can be used to establish a lower bound on solution SIC as per Property \ref{property:id-lower}, and in bounded search the upper bound can be further constrained (Property \ref{property:id-upper}).
	\begin{property}[Lower bound]
		When merging groups $g_i,g_j$ with solution costs $C_i,C_j$ to yield group $g_k$, for any solution for this group with cost $C_k$
		\[C_k\geq C_i + C_j\]
		\label{property:id-lower}
	\end{property}
	\begin{proof}
		Assume there would be a solution with $C_k < C_i + C_j$. Taking $C_k^i$ to denote the SIC of agents that used to make up $g_i$ in the solution to $g_k$, without loss of generality $C_k^i < C_i$, which contradicts the optimality of the solution with cost $C_i$ for $g_i$ independent of $g_j$.
	\end{proof}
	\begin{property}[Reduced upper bound]
		In bounded exhaustive search, the sum of costs of groups not being merged can be subtracted from bound $B$ without losing optimality.
		\label{property:id-upper}
	\end{property}
	\subsubsection{Child pruning}
	In the original ICTS formulation all $k$-children are generated in every case because pruning only controls skipping the low-level search, assumed to be the most expensive operation. However, in simple pruning in any case, when there is a conflict between two or more agents at a given ICT node $(c_1,\ldots,c_k)$, in any solution, one or more of the path costs corresponding to these conflicting agents will have to be incremented. This can be explioted by pruning the node's children that do not correspond to the conflicting agents, of which there are often just 2 or 3, drastically improving the (average) branching factor as $k$ increases. By Property \ref{property:ec-incompat}, child pruning is not compatible with enhanced pruning.
	\begin{property}[Incompatibility with enhanced pruning]
		Enhanced pruning combined with child pruning (hereafter E+C pruning) is suboptimal due to the \textit{cascading effect} described in \cite{sharon2011}.
		\label{property:ec-incompat}
	\end{property}

	\begin{figure}[H]
	\centering
	\begin{subfigure}{0.40\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-ep-2}
		\caption{Instance}
		\label{fig:counter-example:a}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-tree}
		\caption{Pruned ICT that is traversed}
		\label{fig:counter-example:b}
	\end{subfigure}
	\caption{Counter-example for E+C pruning}
	\label{fig:counter-example}
\end{figure}
	\begin{proof}
		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$. It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.  Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$. Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality. $(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path. $(r,b)$ will not change either MDD in this node. When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated. By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed. Notice that none of the nodes with SIC 16 in this ICT are a solution, meaning that E+C pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making it suboptimal.
	\end{proof}

	\section{Results}
	\label{experiments}
	To compare the algorithms and variants described above and put them into the context of alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM developed within the peer group\footnote{I want to thank Jonathan Dönszelmann, who worked on M*-based algorithms, for setting up this comparison[TODO: move to thanks note at end]}. The values compared are the fraction of instances solved, and the average runtime per instance. It should be noticed that in the latter, runtimes converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work, the fraction of instances solved is guiding in the analysis of results.
		\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25, 1 team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25, 3 teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75, 1 team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75, 3 teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25, 1 team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25, 3 teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75, 1 team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75, 3 teams}
			\label{fig:75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps on two types of 20x20 grids with a 120s timeout}
		\label{fig:r-probs}
	\end{figure*}

	\restoregeometry
	\subsection{Experimental setup}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists. For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge. This observation informed the creation of a map generator within the peer group with various parameters. Using this map generator, two types of 20x20 grids were generated:
	\begin{enumerate}
		\item 25: a grid with 25\% of tiles being obstacles.
		\item 75: a grid with 75\% of tiles being obstacles. 
	\end{enumerate}
	For each of these types, two sets of maps were generated with between $1$ to $16$ agents and 200 instances generated for each such agent-setting: one set where all agents belong to one team, another in which the agents were divided into three teams (or $1,2$ teams strictly speaking for the datapoints with respectively $1,2$ agents).

@@

	\subsection{Experiment 1: ICTS-based MAPFM algorithms}
	Figure \ref{fig:i-probs} reports the fraction of instances that each algorithm variant solved within the timeout of 120s in different settings. The meaning of the abbreviations used in the legend are as follows:
	\begin{itemize}
		\begin{minipage}{0.45\linewidth}
			\item S: Simple pruning
			\item E: Enhanced pruning
			\item C: Child pruning
		\end{minipage}
		\begin{minipage}{0.45\linewidth}
			\item ID: Independence detection
			\item B: Bounded search
			\item O: Approximate ordered enumeration
		\end{minipage}
	\end{itemize}
	\subsubsection{Analysis}
	Across scenarios, it is seen that typically exhaustive methods outperform ICTS-m algorithms (\ref{fig:i-probs}), with performance being more similar in the 75 maps with more obstructions. In particular on 75 maps with 3 teams (\ref{fig:i-75-3-p}), the performance of ICTS-m+ID (and optional pruning) is seen to outperform bounded exhaustive search as $k$ increases, and some of these also manage to solve a small fraction of problems of 75 maps with 1 team that exhaustive methods cannot within the time-out (\ref{fig:i-75-1-p}).

	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E. Bounded search outperforms unbounded search as expected, given that the former does at most as much work as the latter and often less. Approximate ordering outperforming unordered enumeration is not quite as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}. Simple pruning with child pruning outperforming exhaustive pruning shows the potential of this novel method. In particular as $k$ grows larger and in scenarios with more obstacles (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}), it appears that having to search a smaller ICT is more important in terms of performance than being able to skip the $k$-agent low-level search more often. In the

	The benefit of using ID together with ordered enumeration is less clear. Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID.
	\subsection{Experiment 2: Algorithms for MAPFM}
	Figure \ref{fig:r-probs} reports the fraction of instances solved within 120s by various algorithms for MAPFM. The algorithms are as follows
	\begin{itemize}
		\begin{minipage}{0.49\linewidth}
			\item A*+ID+OD with matching ID and sorted exhaustive matching\cite{bruin2021}
			\item EPEA* with matching ID and sorted exhaustive matching\cite{jong2021}
			\item M* with sorted exhaustive matching\cite{donszelmann2021}
		\end{minipage}
		\hspace{1cm}
		\begin{minipage}{0.40\linewidth}
			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams\cite{baauw2021}.
			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)

		\end{minipage}
	\end{itemize}
	One of the first things that meets the eye is the staggering performance of CBM in all scenarios with one team (\ref{fig:r-25-1-p},\ref{fig:r-75-1-p}), which are equivalent to anonymous MAPF problems. This can adequately be explained by CBM solving single teams as anonymous MAPF instances in polynomial time, meaning that solving a single team reduces to a polynomial-time procedure (SSP to be specific). It is expected that conform the results reported in \cite{ma2016}, as the number of teams approaches $k$, CBM performance will deteriorate and thus become more similar to the results for exhaustive methods here reported.
	\section{Discussion}
	Although no bound-value data was recorded, one explanation might be that often, early on in the search, single matchings with low $\Delta_m$ are found, causing the rest of the searches to be significantly curtailed. Mo
	However, closer analysis of performance differences between these pruning strategies and alternatives  (repeated enhanced pruning or pruning with pairs, quadruples, etc.) across different scenarios is something for further research.
%	Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
	\section{Conclusions}
	The goal of this research was to seek alternative approaches to solving MAPFM based on ICTS. In this, the research has succeeded, but the scalability of the algorithms leaves something to be desired. Exhaustive methods, like those discussed in detail in \ref{exhaustive}, cannot be expected to scale well as teams grow larger due to their complexity, no matter what optimizations are put in place. Nonetheless, as was shown in Section \ref{experiments}, the more advanced exhaustive ICTS algorithms consistently outperform the ICTS-m based algorithms. It was also seen that in turn a SIC-adaptation of the CBM method \cite{ma2016} greatly outperforms exhaustive alternatives in the settings that were tried out. Therefore, it can be concluded that the method that arguably has the most potential to scale well, ICTS-m, has a long way to go before being usable in practical scenarios with significant problem sizes.
	\section{Future work}
	In this project, there were many roads not taken. In particular for the ICTS-m variant, there are still many things that could be experimented with in order to improve performance, such as more extensive or multi-staged pruning procedures or ways to exploit the fact that agents are partitioned into teams. For instance, the hungarian algorithm could be used to find lower-bounds for per-team SICs, which allows skipping the low-level search in many cases and can trivially be combined with pruned child generation branching within teams.

@@

	\printbibliography
	\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25, 1 team}
			\label{fig:i-25-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25, 3 teams}
			\label{fig:i-25-3}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75, 1 team}
			\label{fig:i-75-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75, 3 teams}
			\label{fig:i-75-3}
		\end{subfigure}
		\caption{Average solving time of different ICTS-based algorithms}
		\label{fig:i-times}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25, 1 team}
			\label{fig:r-25-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25, 3 teams}
			\label{fig:r-25-3}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75, 1 team}
			\label{fig:r-75-1}
		\end{subfigure}
		\begin{subfigure}{0.44\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75, 3 teams}
			\label{fig:r-75-3}
		\end{subfigure}
		\caption{Average solving time of MAPFM algorithms}
		\label{fig:r-times}
	\end{figure*}
